---
title: "Markdown-Module4"
author: "Me"
date: "9/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Final code with peer edits (see peer edits and original code below, ps: it's a mess cause I didn't understand Rmarkdown)

Challenge 1
```{r}
line<-"Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
library(stringr)
line5<-strsplit(line, " ")[[1]]
line5
line6<-matrix(line5, nrow = 7, ncol = 3, byrow = TRUE)
line6
line6[1:7,3]
```
Challenge 2
```{r}
a<-array(400:1, dim = c(5,5,4,4))
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```
Challenge 3
```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m
x1<-m[1:8,2:3]
x1
x2<-m[1:8,6]
x2
x3<-cbind(x1, x2)
x3
x4<-m[6:8,]
x4
x5<-m[2:6, 2:9]
x5
```
Challenge 4
```{r}
Platyrrhini<-list("Cebidae, Atelidae, Pitheciidae")
Catarrhini<-list("Cercopithecidae, Hylobatidae, Hominidae")
Tarsioidea<-list("Tarsiidae")
Lorisoidea<-list("Lorisidea, Galagidae")
Lemuroidea<-list("Cheirogaleidae, Lepilemuridae, Indriidae, Lemuridae, Daubentoniidae")
Haplorhini=c(Anthropoidea=c(Catarrhini=c(Catarrhini), Platyrrhini=c(Platyrrhini)), Tarsioidea = c("Tarsiidae"))
Haplorhini
Strepsirhini=c(Lorisoidea=c(Lorisoidea), Lemuroidea=c(Lemuroidea))
Primates = c(Haplorhini=c(Anthropoidea=c(Catarrhini=c(Catarrhini), Platyrrhini=c(Platyrrhini)), Tarsioidea = c("Tarsiidae")), Strepsirhini=c(Lorisoidea=c(Lorisoidea), Lemuroidea=c(Lemuroidea)))
Primates
```
Challenge 5
```{r}
matrix<-matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
matrix
frame<-data.frame(matrix)
frame
str(frame)
dim(frame)
colnames(frame)
sapply(frame, class)
frame[["X1"]]
frame2<-data.frame(as.numeric(frame$X1), as.logical(frame$X2), as.factor(frame$X3))
frame2
str(frame2)
#this code has a bunch of stuff where I am just looking at what my data frame consists of and the variable types so I could make sure things were going alright. My first code didn't maintain the correct numeric values. 
```




<<<<<<< HEAD
Challenge 1
```{r}
line<-"Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
=======

#Challenge 1

####All your code should be in chunks,like the one a made below. Click on the insert button above to create a chunk and them paste the code in it. See my Rmarkdown if you want an example.######
```{r}
line<-"Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
```

>>>>>>> 7d86a141553940984e122a7e114ffd93f10fe721
#This places the quote into R, but this quote is a singular attribute and not a string of separate words
library(stringr)
#Uploaded the stringr from my library so I can use it
line2<-str_split(line, boundary("word"))
#line is the subject that I want to split, boundary represents how I want to split up the sentence. In this case I want to split the sentenced based on words.
#I named this line 2
mode(line2)
#this tells me that I have a list...
length(line2)
#hmmm I don't really want this. The elements of the line 2 are not separated
line2
line3<-list(line2)
line3
#somehow we got rid of punctuation so yay?
length(line3)
#still has a length of 1?
str(line3)
#well now I now there are 22 characters/words
line3[1]
#lets go back to using line2 shall we?
line2
line4<-c(line2)
line4
#that didn't do anything...We need a character vector
line5<-strsplit(line, " ")[[1]]
#DID THIS JUsT WORKKKKKKKK?????
line5
#Yes this turned my string into a vector made of individual words.
#Ok, now I need to turn this vector into a matrix, or maybe an array?
line6<-matrix(line5, nrow = 7, ncol = 3)
#awesome. Now we have a matrix. We are missing one word but tbh I don't need it cause it would have appear in column 1 and I want column 3 values
line6[1:7,3]
#So now we have extracted every third word! WOHOOO
#FINAL CODE
line<-"Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed."
library(stringr)
line5<-strsplit(line, " ")[[1]]
line5
<<<<<<< HEAD
line6<-matrix(line5, nrow = 7, ncol = 3, byrow = TRUE)
line6
line6[1:7,3]
#Fix: I forgot to fill in the columns rowwise, but that was an easy fix. Also I know the error is saying I'm ommiting a word, but we don't care about that word since its not in the third column. 
```
Challenge 2
```{r}
=======
line6<-matrix(line5, nrow = 7, ncol = 3)
line6[1:7,3]
######Im sorry but you are getting the wrong words here. The problem is that you are spliting your data into 7 rows and 3 columns so when you do line6[1:7,3] you are actually getting the 3 word in each row. Try to put every word in its own row and get every 3rd row######

#Challenge 2
>>>>>>> 7d86a141553940984e122a7e114ffd93f10fe721
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m
#So this is what we were given to start with
x1<-m[1:8,2:3]
x1
x2<-m[1:8,6]
x2
x3<-cbind(x1, x2)
#Now that we have created two matrices with the values we want we combined them.
#Next we need to extract rows 6 to 8
x4<-m[6:8,]
x4
#awesome! that was easy. 
#Lastly we need elments from [2,2] to [6, 9]
x5<-m[2:6, 2:9]
x5
#wonderful, am done. 
#FINAL CODE
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m
x1<-m[1:8,2:3]
x1
x2<-m[1:8,6]
x2
x3<-cbind(x1, x2)
x3
x4<-m[6:8,]
x4
x5<-m[2:6, 2:9]
x5
<<<<<<< HEAD
```
Challenge 3
```{r}
=======
######this is more or less like mine. Looks good!########

#Challenge 3
>>>>>>> 7d86a141553940984e122a7e114ffd93f10fe721
a<-array(400:1, dim = c(5,5,4,4))
a
#Now we have our array with the first part specifying our numeric variables that will occur within the array and the dim expressing the four dimensions of the array
a[1, 1, 1, 2]
#This matrix specifies 300, a point found that the specific array coordinates listed.
a[2, 3, 2, ]
#This matrix specifies the first three coordinates, but say that any value that is found within these
#coordinates is selected. So anything in the fourth array perameters is selected. The results yield
#364, 264, 164, and 64. Essentially every 100 attributes. 
a[1:5, 1:5, 3, 3]
#This matrix is set up so that a subset of matrix data is taken from the array. 
<<<<<<< HEAD
#We have matrix 3,3 with rows 1-5 and columns 1-5.
#FINAL CODE
a<-array(400:1, dim = c(5,5,4,4))
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```
Challenge 4
```{r}
=======
#We have matrix 3,3 with rows 1-5 and columns 1-5. 
#######Got the same thing!! Yay!########3

#Challenge 4
>>>>>>> 7d86a141553940984e122a7e114ffd93f10fe721
Platyrrhini<-list("Cebidae, Atelidae, Pitheciidae")
Catarrhini<-list("Cercopithecidae, Hylobatidae, Hominidae")
Anthropoidea<-list(Catarrhini, Platyrrhini)
Tarsioidea<-list("Tarsiidae")
Haplorhini<-list(Anthropoidea, Tarsioidea)
Lorisoidea<-list("Lorisidea, Galagidae")
Lemuroidea<-list("Cheirogaleidae, Lepilemuridae, Indriidae, Lemuridae, Daubentoniidae")
Strepsirhini<-list(Lorisoidea, Lemuroidea)
primates<-list(Haplorhini, Strepsirhini)
primates
#this was my first attempt at a list. It created the list but will not desplay all the names only the levels. 
primates<- list(names(Haplorhini, Strepsirhini)
#going backwards did not work
Platyrrhini<-c("Cebidae, Atelidae, Pitheciidae")
Platyrrhini
#this level is now listed out
Catarrhini<-c("Cercopithecidae, Hylobatidae, Hominidae")
Catarrhini
#this level is now listed out 
#ok this is is gonna be a loooonnnggg line of code.                 
Haplorhini=c(Anthropoidea=c(Catarrhini=c(Catarrhini), Platyrrhini=c(Platyrrhini)), Tarsioidea = c("Tarsiidae"))
Haplorhini
Strepsirhini=c(Lorisoidea=c(Lorisoidea), Lemuroidea=c(Lemuroidea))
Primates = c(Haplorhini=c(Anthropoidea=c(Catarrhini=c(Catarrhini), Platyrrhini=c(Platyrrhini)), Tarsioidea = c("Tarsiidae")), Strepsirhini=c(Lorisoidea=c(Lorisoidea), Lemuroidea=c(Lemuroidea)))
Primates
#so this kinda worked? Not sure how to format so that the list appears nice and organized by levels. 
#FINAL CODE
Platyrrhini<-list("Cebidae, Atelidae, Pitheciidae")
Catarrhini<-list("Cercopithecidae, Hylobatidae, Hominidae")
Tarsioidea<-list("Tarsiidae")
Lorisoidea<-list("Lorisidea, Galagidae")
Lemuroidea<-list("Cheirogaleidae, Lepilemuridae, Indriidae, Lemuridae, Daubentoniidae")
Haplorhini=c(Anthropoidea=c(Catarrhini=c(Catarrhini), Platyrrhini=c(Platyrrhini)), Tarsioidea = c("Tarsiidae"))
Haplorhini
Strepsirhini=c(Lorisoidea=c(Lorisoidea), Lemuroidea=c(Lemuroidea))
Primates = c(Haplorhini=c(Anthropoidea=c(Catarrhini=c(Catarrhini), Platyrrhini=c(Platyrrhini)), Tarsioidea = c("Tarsiidae")), Strepsirhini=c(Lorisoidea=c(Lorisoidea), Lemuroidea=c(Lemuroidea)))
Primates
<<<<<<< HEAD
```
Challenge 5
```{r}
=======
######This is very clever. I couldn't quite figure out what he wanted but this is better than what I came up with.######

#CHallenge 5
>>>>>>> 7d86a141553940984e122a7e114ffd93f10fe721
matrix<-matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
matrix
#our matrix is create and filled by row. 
frame<-as.data.frame(as.matrix(matrix))
frame
#our matrix is now a data frame
V2<-data.frame(V1 = as.numeric(1:5), V2 = as.logical(1:5), V3 = as.numeric(1:5), stringsAsFactors = FALSE)
V2
str(V2)
#V2 has now been turned into a logical type. I had to specify the type of each variable. 
V3<-data.frame(V1 = as.numeric(1:5), V2 = as.numeric(1:5), V3 = as.factor(1:5), stringsAsFactors = FALSE)
V3
str(V3)
#FINAL CODE
matrix<-matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
matrix
<<<<<<< HEAD
frame<-data.frame(matrix)
frame
str(frame)
dim(frame)
colnames(frame)
sapply(frame, class)
frame[["X1"]]
frame2<-data.frame(as.numeric(frame$X1), as.logical(frame$X2), as.factor(frame$X3))
frame2
str(frame2)
#I fixed this code finally! I changed the data types but I also did this by putting them into a new data frame. Basically converting from one data frame to another with data.frame() function. One thing I am unclear about is why the column names changed or how to change them back to not so long names.  
```
=======
frame<-as.data.frame(as.matrix(matrix))
frame
V2<-data.frame(V1 = as.numeric(1:5), V2 = as.logical(1:5), V3 = as.numeric(1:5), stringsAsFactors = FALSE)
V2
str(V2)
V3<-data.frame(V1 = as.numeric(1:5), V2 = as.numeric(1:5), V3 = as.factor(1:5), stringsAsFactors = FALSE)
V3
str(V3)

#####Lots of issues with this one. You are good up to line 168 but then you got off track. The problem is that you replace the data in your table with new numbers by doing this V1 = as.numeric(1:5), V2 = as.numeric(1:5), V3 = as.factor(1:5). Now all your colums have the numbers 1-5 in ascending order. for a vector to be logical it must have only 1's and 0's in it so they can be interpreted as true or false. I could not figur out myself how to permanently coerce the columns but I was able to find a way to read column 2 as logical and column 3 as factors which are like levels.Hope you find this useful!#######
>>>>>>> 7d86a141553940984e122a7e114ffd93f10fe721
